Supplementary Material: District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-08-22 paper/supp_figs.tex
Updates from Overleaf

{\color{red} \bf
To do:
\begin{itemize}
    \item Aggregated areas
    \item Model calibration
    \item Prior choice
    \item Citations
\end{itemize}}

Following a similar approach to \cite{thomas2021multilevel}, we developed a Bayesian hierarchical model with small area estimation methods that uses survey data to estimate the probabilities and coverage of circumcision using a competing risk discrete time-to-event model stratified by region, age, time, and type.

We modelled each country independently rather than a model by sub-region or for the whole of sub-Saharan due to computational constraints and we modelled probabilities of circumcision at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys.

In countries where suitable survey information was collected on circumcision type, we consider the following two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC). In countries that did not have a survey that contained information on the type of circumcision, so we were unable to conduct an analysis of the probabilities of circumcision by type. Therefore, we consider a used survey data to estimates the probabilities and coverage of circumcision of any or (unknown) type (MC).

@@

We used survey data to model the probabilities of receiving a TMC, MMC or MC for individuals residing in region $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.

@@

\noindent We define $\lambda^{\text{TMC}}_{iat}$ as the probability that an individual in region $i$ received TMC at age $a$ and time step $t$, given they were uncircumcised by age $a-1$ and time $t-1$, 
\begin{equation} 
		\lambda^{\text{TMC}}_{iat} = \mathbb{P}(\text{TMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)). 
	\label{eqn::TMC}
\end{equation}
A key assumption of \cite{thomas2021multilevel} model was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa but an assumption of a constant probability of TMC might not be feasible everywhere. For example, in some countries the level and practices of TMC has changed through time due to demographic shifts. There has also been a replacement of TMCs through MMCs observed, particularly in VMMC priority countries, to ensure HIV prevention efficacy and/or for safety considerations \cite{thomas2021multilevel}. Furthermore, there may also be cases where TMC remains stable and allowing a constant probability of TMC in the competing risks framework will cause a reduction in TMC coverage overall in places where VMMC uptake is high. Here, we consider two models for $\lambda^{\text{TMC}}_{iat}$ in each country: (i) time invariant (i.e. constant over time) and (ii) time variant (i.e. varying over time). The {\it time-invariant} probability of TMC was modelled using a piece-wise logit-linear function, 
\begin{equation*} 
	\text{logit}(\lambda^{\text{TMC}}_{iat}) = \hat{\alpha} + \hat{\psi}_i + \hat{\phi}_a + \hat{\gamma}_{ia}
\end{equation*}
where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a regional random effect, $\hat{\phi}_a$ is an age random effect, and $\hat{\gamma}_{ia}$ is an age-space interaction term to allow different age patterns of TMC across regions. The {\it time-variant} probability of TMC was also modelled using a piece-wise logit-linear function, 
\begin{equation*} 
	\text{logit}(\lambda^{\text{TMC}}_{iat}) = \hat{\alpha} + \hat{\psi}_i + \hat{\phi}_a + \hat{\theta}_t + \hat{\gamma}_{ia} + \hat{\delta}_{at}
\end{equation*}
where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a regional random effect, $\hat{\phi}_a$ is an age random effect, $\theta_i$ is a temporal random effect,  $\hat{\gamma}_{ia}$ is an age-space interaction term to allow different age patterns of TMC  across regions and $\hat{\delta}_{at}$ is an age-time interaction term to allow for different age patterns of TMCs over time. We did not include a space-time interaction into due to computational reasons.

@@

\noindent We defined $\lambda^{\text{MMC}}_{iat}$ as the probability an individual in region $i$ received MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,  
\begin{equation*}
		\lambda^{\text{MMC}}_{iat} = \mathbb{P}(\text{MMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)),
\end{equation*}
To ensure $\lambda^{\text{TMC}}_{iat} + \lambda^{\text{MMC}}_{iat} \leq 1$ for all $i$, $a$ and $t$ in the discrete-time framework, we assumed the TMC prior to MMC in each time step. Therefore, we condition on this and practically model the probability an individual in region $i$ received an MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$ and did not receive TMC at age $a$ and time $t$
\begin{equation*}
		\tilde{\lambda}^{\text{MMC}}_{iat} = \mathbb{P}(\text{MMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1) \text{ and no TMC in} \; (i,a, t))
\end{equation*}
It then follows that 
\begin{equation*}
		\lambda^{\text{MMC}}_{iat} = \tilde{\lambda}^{\text{MMC}}_{iat}\cdot (1-\lambda^{\text{TMC}}_{iat}).
\end{equation*}

The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed  since 2008 in countries that have programmes to scale-up MMC for HIV prevention. VMMC programmes provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision often occurs through cultural or religious practices unrelated to scale-up of VMMC for HIV prevention. Due to this, Thomas et al. \cite{thomas2021multilevel} separated the probability of MMC, $\tilde{\lambda}^{\text{MMC}}_{iat}$, into two processes: (i) paediatric circumcision (for those aged 0--9) and (ii) adolescent and adult circumcision (for those aged 10 and over). This ensured that any increase in MMC for those aged 10 and over did not affect the probability of MMC in those under 10 in South Africa. However, this may not be appropriate everywhere, particularly in countries without programmes to upscale MMC coverage. Therefore, we consider two models for $\lambda^{\text{MMC}}_{iat}$ in each country: (i) [Need a name] and (ii) [Need a name].

We modelled $\tilde{\lambda}^{\text{MMC}}_{iat}$ using a piece-wise logit-linear function:

\begin{equation*}
	\text{logit}(\tilde{\lambda}^{\text{MMC}}_{iat}) = \alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} 
\end{equation*}
where $\alpha$ is the intercept, $\psi_i$ is a regional random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-space interaction terms to allow for different patterns of MMCs over age between regions $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MMCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MMCs over time across regions.

Therefore, we modelled $\tilde{\lambda}^{\text{MMC}}_{iat}$ using a piece-wise logit-linear function:
\begin{equation*}
	\text{logit}(\tilde{\lambda}^{\text{MMC}}_{iat}) =
	\begin{cases}
		\bar{\alpha} + \bar{\psi}_i + \bar{\phi}_a + \bar{\gamma}_{ia} & \text{for } 0 \leq a \leq 9\\
		\alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} & \text{for } a \geq 10
	\end{cases} 
\end{equation*}
where $\bar{\alpha}$ and $\alpha$ are intercepts, $\bar{\psi}_i$ and $\psi_i$ are regional random effects, $\theta_i$ are temporal random effects, $\bar{\phi}_a$ and $\phi_a$ are age random effects, $\bar{\gamma}_{ia}$ and $\gamma_{ia}$ are age-space interaction terms to allow for different age patterns of MMCs between regions, for paediatric circumcision and adolescent and adult circumcision respectively. The $\delta_{at}$ is an age-time interaction term to allow for different age patterns of MMCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MMCs over time across regions, in adolescent and adult men. We assume that the probabilities of MMC among those aged 0--9 were constant over time, (i.e. $\lambda^{\text{MMC}}_{iat} \equiv \lambda^{\text{MMC}}_{ia}$ when $0\leq a \leq 9$), as paediatric medical circumcision practices are unrelated to VMMC for HIV prevention and are relatively stable.

The choice of whether a country used a {\color{red}\bf[Need a name]} or {\color{red}\bf[Need a name]} probability of MMC was chosen depending on which produced the best within-sample model fit (see Section \ref{sec::modelcheck} for further details).

@@

Some countries did not have a survey that collected information on the type of circumcision, so we were unable to conduct an analysis of the probabilities of circumcision by type. In this case, we use survey data to model the probabilities of receiving a MC of any type for individuals residing in region $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.

We defined $\lambda^{\text{MC}}_{iat}$ as the probability an individual in region $i$ received a circumcision  at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,  
\begin{equation}
		\lambda^{\text{MC}}_{iat} = \mathbb{P}(\text{MC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)),
	\label{eqn::mc}
\end{equation}
Here, we model $\lambda^{\text{MC}}_{iat}$ using a piece-wise logit-linear function:
\begin{equation*}
	\text{logit}(\lambda^{\text{MC}}_{iat}) = \alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} 
\end{equation*}
where $\alpha$ is the intercept, $\psi_i$ is a regional random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-space interaction terms to allow for different patterns of MCs over age between regions $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MCs over time across regions.

\subsection{Including aggregated estimates}
\label{sec::aggregated}

\begin{equation*}
	\lambda^{\text{MC}}_{Rat} = \frac{\sum_{i\in R}P_{iat}\lambda^{\text{MC}}_{iat}}{\sum_{i\in R}P_{iat}}
\end{equation*}

@@

The probability $S_{iat}$ of remaining uncircumcised up to age $a$ and time $t$,  typically referred to as the survivor function, is expressed as
\begin{equation}
	\begin{split}
		S_{iat} &= \mathbb{P}(\text{Uncircumcised in} \; (i,a-1,t-1)) \\
				&= \prod_{(0,(t-a))}^{(a-1,t-1)}\lambda^{\text{UC}}_{iat} \\
				&= \lambda^{\text{UC}}_{i,0,t-a}\cdot \lambda^{\text{UC}}_{i,1,t-a+1}\cdot\ldots \cdot\lambda^{\text{UC}}_{i,a-1,t-1}
	\end{split}
	\label{eqn::survfunc}
\end{equation}
where $\lambda^{\text{UC}}_{iat}$ is the probability an individual in region $i$ remained uncircumcised at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$, was
\begin{equation*}
	\begin{split}
		\lambda^{\text{UC}}_{iat} &= \mathbb{P}(\text{Uncircumcised in}  \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)),\\
		&= 1 - \lambda^{\text{MC}}_{iat} 
	\end{split}
	\label{eqn::uncirc}
\end{equation*}

The cumulative incidence function (CIF) defines the marginal probability (or coverage/proportion) of individuals who received a TMC, a MMC or a MC of any type by age $a$ and time $t$, accounting for the competing risk of other circumcision types. This was calculated as the sum of incidence of circumcision by type $k$ at each age up to $a$:
\begin{equation*}
	\begin{split}
		\text{CIF}_{iat}^k &= \mathbb{P}(k \; \text{by} \; (i,a,t)) \\
		&= \sum_{(0,(t-a))}^{(a,t)} I^k_{iat}
	\end{split}
	\label{eqn::cuminc}
\end{equation*}
where $I^k_{iat}$ is the incidence of circumcision of type $k\in \{\textrm{TMC}, \textrm{MMC}, \textrm{MC}\}$, in region $i$, at age $a$ and time $t$, 
\begin{equation*}
	\begin{split}
		I_{iat}^k &= \mathbb{P}(k \; \text{in} \; (i,a,t)) \\
		       &= \mathbb{P}(k \; \text{in} \; (i,a,t) | \; \text{Uncircumcised in} \; (i,a-1,t-1))\times \\
		       & \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\mathbb{P}(\text{Uncircumcised in} \; (i,a-1,t-1)) \\
	    	   &= \lambda_{iat}^k \cdot S_{iat} 
	\end{split}
	\label{eqn::inc}
\end{equation*}

@@

In space, we assigned the random effects $\hat{\psi}_i$, $\bar{\psi}_i$, $\psi_i$, $\hat{\gamma}_{ia}$, $\gamma_{ia}$ and $\zeta_{it}$, intrinsic conditional autoregressive (ICAR) priors in space \cite{besag1995conditional}. An ICAR model allows us to encodes spatial dependence between neighbouring regions which allows information on the probability and coverage of circumcision in areas where data is sparse or non-existent to be borrowed. For a generic parameter $\beta_i$, an ICAR model assumes that the mean of $\beta_i$ is a weighted average its neighbours, 
\begin{equation*}
	\beta_i \;|\; \beta_{j}, j \sim i, \tau_{\beta} \sim \text{N}\left(\frac{1}{n_i} \sum_{j \sim i} \beta_j, \frac{1}{n_i\tau_{\beta}} \right) \;\;\; i = 1, 2, 3,\ldots, N_I
\end{equation*}
Here, $j \sim i$ refers to the neighbours of region $i$, $n_i$ is the number of neighbours and $\tau_{\beta}$ is the marginal precision \cite{rue2005gaussian}.

In age, we modelled the random effects ($\hat{\phi}_a$, $\bar{\phi}_a$, $\phi_a$, $\hat{\gamma}_{ia}$, $\bar{\gamma}_{ia}$, $\gamma_{ia}$ and $\delta_{at}$) using penalised B-splines. For a generic parameter $\beta_a$, penalised B-splines assumes that $\beta_a$ is a sum of basis functions, 
\begin{align*} 
	\beta_a = \sum_{j = 1}^{J} w_{j}b_{aj}
\end{align*} 
where $b_{aj}$ are B-spline basis functions {\color{red}[CITE]} with knots placed every five years (at 0, 5, 10 etc.), $J$ is the number of splines used and $\omega_{j}$ are the spline weight parameters to be estimated. The weights $w_{j}$ are penalised using an AR1 process 
\begin{align*} 
  w_{j} \; | \; w_{j-1}, \rho_{w}, \tau_{w} &\sim N(\rho_{w} \cdot w_{j-1}, \;\; \tau^{-1}_{w}) \;\;\;  j = 2, 3,\ldots, J \\
  w_{1} \; | \; \rho_{w}, \tau_{w} &\sim N(0, \tau^{-1}_{w}) 
\end{align*}
where $|\rho_{w}| < 1$ is an autocorrelation parameters controlling the correlation of the effect of the current age on the previous age and $\tau_{w}$ is the precision.

In time, we consider three possible prior distirbution choices: an autoregressive process of order 1 (AR1), random walk of order 1 (RW1) and random walk of order 2 (RW2). {\color{red} \bf [Need more information]}
% \noindent In time, we assigned the random effects $\theta_t$, $\delta_{at}$ and $\zeta_{it}$ an autoregressive process of order 1 (AR1) priors,
\begin{align*} 
  \beta_{t} \; | \; \beta_{t-1}, \rho_{\beta}, \tau_{\beta} &\sim N(\rho_{\beta} \cdot \beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\;  t = 2, 3,\ldots, N_T \\
  \beta_{1} \; | \; \rho_{\beta}, \tau_{\beta} &\sim N(0, \tau^{-1}_{\beta})  \;\;\;  t = 1
\end{align*}

\begin{align*} 
  \beta_{t} \; | \; \beta_{t-1}, \tau_{\beta} &\sim N(\beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\;  t = 2, 3,\ldots, N_T \\
  \beta_{1} \; | \; \rho_{\beta}, \tau_{\beta} &\sim N(0, \tau^{-1}_{\beta})  \;\;\;  t = 1
\end{align*}

\begin{align*} 
  \beta_{t} \; | \; \beta_{t-1}, \tau_{\beta} &\sim N(\beta_{t-1}, \;\; \tau^{-1}_{\beta}) \;\;\;  t = 3, 4,\ldots, N_T \\
  \beta_{t} \; | \; \rho_{\beta}, \tau_{\beta} &\sim N(0, \tau^{-1}_{\beta})  \;\;\;  t = 1, 2
\end{align*}

% where $|\rho_{\phi}| < 1$ is an autocorrelation parameters controlling the correlation of the effect of the current age on the previous age and $\tau_{\beta}$ is the precision.

Moreover, age-space, age-time, and space-time interaction terms ($\hat{\gamma}_{ia}$, $\bar{\gamma}_{ia}$, $\gamma_{ia}$, $\delta_{at}$ and $\zeta_{it}$) are modelled using a Type IV interactions as defined by Knorr-Held and Leonard \cite{knorr2000bayesian},

>>>>

{\color{red} \bf
To do:
\begin{itemize}
    \item Model calibration
    \item Prior choice
    \item Citations
\end{itemize}}

Following a similar approach to \cite{thomas2021multilevel}, we developed a Bayesian hierarchical model with small area estimation methods that uses survey data to estimate the probabilities and coverage of circumcision using a competing risk discrete time-to-event model stratified by region, age, time, and type. We modelled each country independently rather than a model by sub-region or for the whole of sub-Saharan due to computational constraints and we modelled probabilities of circumcision at the organizational level in which the country team has prioritised their program, called the PSNU area level, or the most granular level available in surveys (hereafter called the district-level).

In countries where suitable survey information was collected on circumcision type, we consider the following two types of circumcision: (1) circumcisions that occurred in traditional male initiation ceremonies or for other religious or cultural reasons (TMC) and (2) circumcisions for non-traditional reasons and/or HIV prevention that take place in a clinical setting using medical methods (MMC). Some countries did not have any surveys that collected information on the type of circumcision (see above), so we were unable to conduct an analysis of the probabilities of circumcision by type. For these countries, we consider estimating the probability and coverage of circumcision of any or (unknown) type (MC) only.

@@

In countries where suitable survey information was collected on circumcision type, we used survey data to model the probabilities of receiving a TMC, MMC or MC for individuals residing in district $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.

@@

\noindent We define $\lambda^{\text{TMC}}_{iat}$ as the probability that an individual in district $i$ received TMC at age $a$ and time step $t$, given they were uncircumcised by age $a-1$ and time $t-1$, 
\begin{equation} 
		\lambda^{\text{TMC}}_{iat} = \mathbb{P}(\text{TMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)). 
	\label{eqn::TMC}
\end{equation}
A key assumption of the \cite{thomas2021multilevel} model was that TMC was constant over time, due to traditional male initiation ceremonies amongst tribal, cultural and religious groups remained stable over time in South Africa however an assumption of a constant probability of TMC might not be feasible everywhere. For example, in some countries the level and practices of TMC have changed through time due to demographic shifts. There has also been a replacement of TMCs through MMCs observed, particularly in VMMC priority countries, to ensure HIV prevention efficacy and/or for safety considerations \cite{thomas2021multilevel}. Furthermore, there may also be cases where TMC remains stable and allowing a constant probability of TMC in the competing risks framework will cause a reduction in TMC coverage overall in places where VMMC uptake is high. Here, we consider two models for $\lambda^{\text{TMC}}_{iat}$ in each country: (i) time invariant (i.e. constant over time) and (ii) time variant (i.e. varying over time).

The {\it time-invariant} probability of TMC was modelled using a piece-wise logit-linear function, 
\begin{equation*} 
	\text{logit}(\lambda^{\text{TMC}}_{iat}) = \hat{\alpha} + \hat{\psi}_i + \hat{\phi}_a + \hat{\gamma}_{ia}
\end{equation*}
where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a district random effect, $\hat{\phi}_a$ is an age random effect, and $\hat{\gamma}_{ia}$ is an age-district interaction term to allow different age patterns of TMC across districts. The {\it time-variant} probability of TMC was also modelled using a piece-wise logit-linear function, 
\begin{equation*} 
	\text{logit}(\lambda^{\text{TMC}}_{iat}) = \hat{\alpha} + \hat{\psi}_i + \hat{\phi}_a + \hat{\theta}_t + \hat{\gamma}_{ia} + \hat{\delta}_{at}
\end{equation*}
where $\hat{\alpha}$ is the intercept, $\hat{\psi_i}$ is a district random effect, $\hat{\phi}_a$ is an age random effect, $\theta_i$ is a temporal random effect,  $\hat{\gamma}_{ia}$ is an age-district interaction term to allow different age patterns of TMC across districts and $\hat{\delta}_{at}$ is an age-time interaction term to allow for different age patterns of TMCs over time. We did not include a district-time interaction into due to computational constraints.

@@

\noindent We defined $\lambda^{\text{MMC}}_{iat}$ as the probability an individual in district $i$ received MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,  
\begin{equation*}
		\lambda^{\text{MMC}}_{iat} = \mathbb{P}(\text{MMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)),
\end{equation*}
To ensure $\lambda^{\text{TMC}}_{iat} + \lambda^{\text{MMC}}_{iat} \leq 1$ for all $i$, $a$ and $t$ in the discrete-time framework, we assumed the TMC prior to MMC in each time step. Therefore, we condition on this and practically model the probability an individual in district $i$ received an MMC at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$ and did not receive TMC at age $a$ and time $t$
\begin{equation*}
		\tilde{\lambda}^{\text{MMC}}_{iat} = \mathbb{P}(\text{MMC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1) \text{ and no TMC in} \; (i,a, t))
\end{equation*}
It then follows that 
\begin{equation*}
		\lambda^{\text{MMC}}_{iat} = \tilde{\lambda}^{\text{MMC}}_{iat}\cdot (1-\lambda^{\text{TMC}}_{iat}).
\end{equation*}

The provision of MMC is highly heterogeneous in sub-Saharan Africa and has changed substantially since 2008, particularly in countries that have programmes to scale-up MMC for HIV prevention. VMMC programmes provide MMCs for HIV prevention to those aged 10 and over, while infant and paediatric medical circumcision often occurs through cultural or religious practices unrelated to scale-up of VMMC for HIV prevention. Due to this, Thomas et al. \cite{thomas2021multilevel} separated the probability of MMC, $\tilde{\lambda}^{\text{MMC}}_{iat}$, into two processes: (i) paediatric circumcision (for those aged 0--9) and (ii) adolescent and adult circumcision (for those aged 10 and over). This ensured that any increase in MMC for those aged 10 and over did not bias the probability of MMC in those under 10 in South Africa. However, this may not be appropriate everywhere, particularly in countries without programmes to upscale MMC coverage. Therefore, we consider two models for $\lambda^{\text{MMC}}_{iat}$ in each country: (i) no cut-off and (ii) paediatric cut off.

We modelled the probability of MMC {\it with no cut-off} using a piece-wise logit-linear function, 
\begin{equation*}
	\text{logit}(\tilde{\lambda}^{\text{MMC}}_{iat}) = \alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} 
\end{equation*}
where $\alpha$ is the intercept, $\psi_i$ is a district random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-district interaction terms to allow for different patterns of MMCs over age between districts, $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MMCs over time and $\zeta_{it}$ is an district-time interaction term to allow for different uptake of MMCs over time across districts. We also modelled the probability of MMC {\it with a paediatric cut-off} using a piece-wise logit-linear function, 
\begin{equation*}
	\text{logit}(\tilde{\lambda}^{\text{MMC}}_{iat}) =
	\begin{cases}
		\bar{\alpha} + \bar{\psi}_i + \bar{\phi}_a + \bar{\gamma}_{ia} & \text{for } 0 \leq a \leq 9\\
		\alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} & \text{for } a \geq 10
	\end{cases} 
\end{equation*}
where $\bar{\alpha}$ and $\alpha$ are intercepts, $\bar{\psi}_i$ and $\psi_i$ are district random effects, $\theta_i$ are temporal random effects, $\bar{\phi}_a$ and $\phi_a$ are age random effects, $\bar{\gamma}_{ia}$ and $\gamma_{ia}$ are age-district interaction terms for paediatric circumcision and adolescent and adult circumcision respectively. The $\delta_{at}$ is an age-time interaction term to allow for different age patterns of MMCs over time and $\zeta_{it}$ is an space-time interaction term to allow for different uptake of MMCs over time across districts in adolescent and adult men. We assume that the probability of MMC among those aged 0--9 were constant over time, (i.e. $\lambda^{\text{MMC}}_{iat} \equiv \lambda^{\text{MMC}}_{ia}$ when $0\leq a \leq 9$), as paediatric medical circumcision practices are unrelated to VMMC for HIV prevention and are relatively stable.

The choice of whether a country used a paediatric cut-off or no cut-off in the probability of MMC was chosen depending on which produced the best within-sample model fit (see Section \ref{sec::modelcheck} for further details).

@@

In countries that did not have a survey that contained information on the type of circumcision, we used survey data to model the probabilities of receiving a MC of any (or unknown) type for individuals residing in district $i \in I = \{1, 2, \ldots, N_I\}$ at age $a \in A = \{0, 1, 2, \ldots, N_A\}$ and time $t \in T = \{1, 2, \ldots, N_T\}$.

\noindent We define $\lambda^{\text{MC}}_{iat}$ as the probability that an individual in district $i$ received a circumcision (either a TMC or MMC) at age $a$ and time step $t$, given they were uncircumcised by age $a-1$ and time $t-1$, 
\begin{equation} 
		\lambda^{\text{MC}}_{iat} = \mathbb{P}(\text{MC} \; \text{in} \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)). 
	\label{eqn::MC}
\end{equation}
We modelled the probability of MC using a piece-wise logit-linear function:
\begin{equation*}
	\text{logit}(\lambda^{\text{MC}}_{iat}) = \alpha + \psi_i + \phi_a + \theta_t + \gamma_{ia} + \delta_{at} + \zeta_{it} 
\end{equation*}
where $\alpha$ is the intercept, $\psi_i$ is a district random effect, $\theta_i$ is a temporal random effect, $\phi_a$ is an age random effect, $\gamma_{ia}$ is an age-district interaction terms to allow for different patterns of MCs over age between districts, $\delta_{at}$ is an age-time interaction term to account for any changing age patterns in MCs over time and $\zeta_{it}$ is an district-time interaction term to allow for different uptake of MCs over time across districts.

@@

We define the probability of remaining uncircumcised, $S_{iat}$, in district $i$, at age $a$ and time $t$ (often called the survivor function), is estimated using, 
\begin{equation*}
	\begin{split}
		S_{iat} &= \mathbb{P}(\text{Uncircumcised in} \; (i,a-1,t-1)) \\
				&= \prod_{(0,(t-a))}^{(a-1,t-1)}\lambda^{\text{UC}}_{iat} \\
				&= \lambda^{\text{UC}}_{i,0,t-a}\cdot \lambda^{\text{UC}}_{i,1,t-a+1}\cdot\ldots \cdot\lambda^{\text{UC}}_{i,a-1,t-1}
	\end{split}
	\label{eqn::survfunc}
\end{equation*}
where $\lambda^{\text{UC}}_{iat}$ is the probability an individual in district $i$ remained uncircumcised at age $a$ and time $t$, given they were uncircumcised by age $a-1$ and time $t-1$,
\begin{equation*}
	\begin{split}
		\lambda^{\text{UC}}_{iat} &= \mathbb{P}(\text{Uncircumcised in}  \; (i,a,t) \; | \; \text{Uncircumcised in} \; (i,a-1, t-1)),\\
		&= 1 - \lambda^{\text{MC}}_{iat} 
	\end{split}
	\label{eqn::uncirc}
\end{equation*}

The cumulative incidence function (CIF) defines the marginal probability (or coverage/proportion) of individuals residing in district $i$ who received a TMC, MMC or MC of any (or unknown) type by age $a$ and time $t$, accounting for the competing risk of other circumcision types. This was calculated as the sum of incidence of circumcision by type $k$ at each age up to $a$:
\begin{equation*}
	\begin{split}
		\text{CIF}_{iat}^k &= \mathbb{P}(k \; \text{by} \; (i,a,t)) \\
		&= \sum_{(0,(t-a))}^{(a,t)} I^k_{iat}
	\end{split}
	\label{eqn::cuminc}
\end{equation*}
where $I^k_{iat}$ is the incidence of circumcision of type $k\in \{\textrm{TMC}, \textrm{MMC}, \textrm{MC}\}$, in region $i$, at age $a$ and time $t$, 
\begin{equation*}
	\begin{split}
		I_{iat}^k &= \mathbb{P}(k \; \text{in} \; (i,a,t)) \\
		       &= \mathbb{P}(k \; \text{in} \; (i,a,t) | \; \text{Uncircumcised in} \; (i,a-1,t-1))\times \\
		       & \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\mathbb{P}(\text{Uncircumcised in} \; (i,a-1,t-1)) \\
	    	   &= \lambda_{iat}^k \cdot S_{iat} 
	\end{split}
	\label{eqn::inc}
\end{equation*}

@@

In space, we assigned the random effects $\hat{\psi}_i$, $\bar{\psi}_i$, $\psi_i$, $\hat{\gamma}_{ia}$, $\gamma_{ia}$ and $\zeta_{it}$, intrinsic conditional autoregressive (ICAR) priors \cite{besag1995conditional}. An ICAR model allows us to encode spatial dependence between neighbouring regions which allows information on the probability and coverage of circumcision in areas where data is sparse or non-existent to be borrowed. For a generic parameter $\beta_i$, an ICAR model assumes that the mean of $\beta_i$ is a weighted average its neighbours, 
\begin{equation*}
	\beta_i \;|\; \beta_{j}, j \sim i, \tau_{\beta} \sim \text{N}\left(\frac{1}{n_i} \sum_{j \sim i} \beta_j, \frac{1}{n_i\tau_{\beta}} \right) \;\;\; i = 1, 2, 3,\ldots, N_I
\end{equation*}
Here, $j \sim i$ refers to the neighbours of region $i$, $n_i$ is the number of neighbours and $\tau_{\beta}$ is the marginal precision \cite{rue2005gaussian}. The joint distribution may be equivalently expressed as $\boldsymbol{\beta} \sim N(\boldsymbol{0}, \tau_{\beta}^{-1}Q^{-1}_{I})$ where $Q_{I}$ is the precision matrix encoding the adjacency structure of the neighbourhoods. The precision matrix $Q_{I}$ is rank deficient and consequently the prior is improper \cite{rue2005gaussian}.

In age, we modelled the random effects ($\hat{\phi}_a$, $\bar{\phi}_a$, $\phi_a$, $\hat{\gamma}_{ia}$, $\bar{\gamma}_{ia}$, $\gamma_{ia}$ and $\delta_{at}$) using penalised B-splines. This allows us to smooth across the age of circumcision profile and also allows information on the probability and coverage of circumcision for ages to be borrowed where the data is sparse or non-existent (i.e. older age groups). For a generic parameter $\beta_a$, penalised B-splines assumes that $\beta_a$ is a sum of basis functions, 
\begin{align*} 
	\beta_a = \sum_{j = 1}^{J} w_{j}b_{aj}
\end{align*} 
where $b_{aj}$ are B-spline basis functions {\color{red}[CITE]} with knots placed every five years (at 0, 5, 10 etc.), $J$ is the number of splines used and $w_{j}$ are the spline weight parameters to be estimated. The weights $w_{j}$ are penalised using an AR1 process, 
\begin{align*} 
  w_{j} \; | \; w_{j-1}, \rho_{w}, \tau_{w} &\sim N(\rho_{w} \cdot w_{j-1}, \;\; \tau^{-1}_{w}) \;\;\;  j = 2, 3,\ldots, J \\
  w_{1} \; | \; \rho_{w}, \tau_{w} &\sim N(0, \tau^{-1}_{w}) 
\end{align*}
where $|\rho_{w}| < 1$ is an autocorrelation parameter controlling the correlation of the effect of the current age on the previous age and $\tau_{w}$ is the precision. The joint distribution is given by $\boldsymbol{w}\; | \; \rho_{w}, \tau_{w} \sim N(\boldsymbol{0}, \tau_{w}^{-1}Q^{-1}_{J}(\rho_{w}))$ where $Q_{J}$ is the precision matrix as defined by the basis functions and the autocorrelation parameter. Then defining $\boldsymbol{\beta} = W_{\beta}\cdot \boldsymbol{w}$ where $W_{\beta}$ is a design matrix evaluating the basis functions $b_{aj}$ at each age of interest, the joint distribution is given by, $\boldsymbol{\beta}\; | \;\boldsymbol{\omega}, \; W_{\beta}, \; \rho_{w}, \tau_{\beta} \sim N(\boldsymbol{0}, \tau_{\beta}^{-1}Q^{-1}_{A})$ where Q^{-1}_{A} = W_{\beta}\cdot Q^{-1}_{J}(\rho_{w})\cdot W_{\beta}^T.
